---
title: "DSjobtracker"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(wordcloud)
library(wordcloud2)
library(tm)
library(RColorBrewer)
library(stringr)
#devtools::install_github("thiyangt/DSjobtracker")
library(DSjobtracker)
data("DStidy_2021")
df <- DStidy_2021
```

Overview
======================================================
Column
-----------------------------------------------------------------------

### *Job Title*
```{r}
jbs <- str_to_lower(df$Job_title)
jbs <- gsub("[[:punct:]]"," ",jbs)


docs1 <- Corpus(VectorSource(jbs))
docs1 <-docs1 %>% tm_map(removePunctuation) %>%  tm_map(removeWords,c("and", "–"))


dtm1 <-  TermDocumentMatrix(docs1)
matrix1 <- as.matrix(dtm1)
words1 <- sort(rowSums(matrix1),decreasing = TRUE)

jbstitle <- data.frame(word1= names(words1),freq1 =words1)

set.seed(500)

wordcloud(words = jbstitle$word1,freq = jbstitle$freq1,  min.freq = 2,max.words=35,random.order=FALSE,font=4,family= "serif",root.per=1.5,scale = c(5,1.5),
          colors = brewer.pal(8,"Dark2"))



```

### *Education Qualification* 
```{r}

edu <- str_to_lower(df$Educational_qualifications)
edu <- gsub("[[:punct:]]"," ",edu)

edu <- edu %>% str_replace_all(c(
  "bachelor's" ="bsc",
  "bachelors" = "bsc",
  "bachelor" = "bsc",
  " bachelor" = "bsc",
  "bsc's" ="bsc",
  "master" = "msc",
  "masters"="msc",
  "masterss"="msc",
  "mscs"="msc"
))



docs2 <- Corpus(VectorSource(edu))

docs2 <- tm_map(docs2,removeWords,c("any","etc","with","higher","and","other","such","related","data","field","of"))

dtm2 <-  TermDocumentMatrix(docs2)
matrix2 <- as.matrix(dtm2)
words2 <- sort(rowSums(matrix2),decreasing = TRUE)

eduQua <- data.frame(word2= names(words2),freq2 =words2)

set.seed(2017)

wordcloud(words = eduQua$word2,freq = eduQua$freq2,  min.freq = 2,max.words=45, random.order=FALSE,font=4,family= "serif",root.per=1.5,scale = c(5,1.5),
          colors = brewer.pal(8,"Dark2"))


```


Column
-----------------------------------------------------------------------

### *Knowledge Base* 
```{r}


knw <- df$Knowledge_in

docs3 <- Corpus(VectorSource(knw))
docs3 <- docs3 %>% tm_map(removePunctuation)
docs3 <- tm_map(docs3,removeWords,c("with"," knowledge","and","from","for","the","large"," etl ","using","that","our","strong","including","methods"))

dtm3 <-  TermDocumentMatrix(docs3)
matrix3 <- as.matrix(dtm3)
words3 <- sort(rowSums(matrix3),decreasing = TRUE)

knwBase <- data.frame(word3= names(words3),freq3 =words3)



wordcloud(words = knwBase$word3,freq = knwBase$freq3, min.freq = 2,max.words=35, random.order=FALSE,font=4,family= "serif",root.per=1.5,scale = c(5,1.5),
          colors = brewer.pal(8,"Dark2"))


```

### *Company Location* 

```{r}
# Data Cleaning 
df$Location[df$Location == "110 Healthy Way, Folosm, CA"] <- "US"
df$Location[df$Locationn == "United Kingdom"] <- "UK"
df$Location[df$Location == "Sri Lnaka"] <- "Sri Lanka"
df$Location[df$Location == "SL"] <- "Sri Lanka"
df$Location[df$Location == "Bloomington, IN"  ] <- "US"
df$Location[df$Location == "Edinburgh,London,Manchester"] <- "UK"
df$Location[df$Location == "Nodia,Uttar Pradesh,India"] <- "India"
df$Location[df$Location == "Melbone" ] <-  "Australia"
df$Location[df$Location == "canada"] <- "Canada "
df$Location[df$Location == "Pennsylvania" ] <- "US"  
df$Location[df$Location == "united states"] <-  "US" 
df$Location[df$Location ==  "Sri lanka" ] <- "Sri Lanka"
df$Location[df$Location == "NewYork"] <- "US"
df$Location[df$Location ==  "Sri lanka" ] <- "Sri Lanka"
df$Location[df$Location == "santa monica,CA" ] <- "US"
df$Location[df$Location ==  "Anaheim, CA"] <- "US"
df$Location[df$Location ==  "Bengaluru, Karnataka, India"] <- "India"
df$Location[df$Location == "United States"  ] <- "US"
df$Location[df$Location ==  "Noida,Uttar Pradesh, India" ] <- "India"
df$Location[df$Location == "Remote Work" ] <- "US"
df$Location[df$Location ==  "USA" ] <- "US"
df$Location[df$Location ==  "Canada " ] <- "Canada"

df$Location[df$Location %>% is.na()] <- "US"

coun <- str_to_upper(df$Location)
coun<- gsub(" ","_",coun)

docs4 <- Corpus(VectorSource(coun))
docs4 <- tm_map(docs4,stripWhitespace)
docs4 <- tm_map(docs4,content_transformer(str_to_title))
dtm4 <-  TermDocumentMatrix(docs4)

matrix4 <- as.matrix(dtm4)
words4 <- sort(rowSums(matrix4),decreasing = TRUE)

loc <- data.frame(word4 = names(words4),freq4 =words4)

set.seed(2017)

wordcloud(words = loc$word4,freq = loc$freq4, min.freq = 2,max.words=16, random.order=FALSE,font=4,family= "serif",root.per=1.5,scale = c(6,1.2),
          colors = brewer.pal(8,"Dark2"))


```


Spatial Distributions
======================================================

```{r  include=FALSE}

data("DStidy_2021")
df <- DStidy_2021

library(flexdashboard)

library(tidyverse)
library(plotly)
library(data.table)
library(countrycode)
library(quantmod)
library(formattable)

#--------------------------------------------------#JOB TYPE

df <- df %>%
  mutate(`Job Type` = case_when(str_detect(df$Job_title, regex("Data analyst", ignore_case=TRUE))~ "Data analyst",
         str_detect(df$Job_title, regex(c("Data scientist","Data science", "science"), ignore_case=TRUE))~ "Data Scientist",
str_detect(df$Job_title, regex("Data Engineer", ignore_case=TRUE))~ "Data Engineer",
str_detect(df$Job_title, regex(c("Business Intelligence", "Business Analyst"), ignore_case=TRUE))~ "BI/BA",
str_detect(df$Job_title, regex( "Statistic", ignore_case=TRUE))~ "Statistician",
TRUE   ~  "Other" ))


df$`Job Type` <- as.factor(df$`Job Type`)


```

Row 
-------------------------------------

### Spatial Distribution of proportion of Job Advertisments
    
```{r Job advertisments map}

new <- df %>%
  select(c(Country, country_code)) %>%
  group_by(country_code) %>%
  count(Country) %>%
  ungroup() %>%
  mutate(Percentage = percent(n/sum(n)))


fig <- plot_ly(new, type='choropleth', locations=new$country_code, z=new$Percentage, text=~paste('Country: ', 
                                                                                                 new$Country, '<br> Count: ', new$n, '<br> Percentage: ',new$Percentage),hoverinfo = 'text',colorscale="Viridis") %>%
        layout(title = "Spatial Distribution of Proportion of Job Advertisments - 2021")

fig


```

### Advertisment Distribution by country

```{r distribution by country}
new %>%
  plot_ly(
  x = ~n,
  y = ~reorder(Country,-desc(n)),
  type = "bar",
  orientation = "h"
  ) %>%
  layout(title = "Distribution of Job Advertisments by Country - 2021",
         yaxis = list(title = "Country"), xaxis = list(title = "Total Number of Advertisments",categoryorder = "n"), barmode = 'stack')
  
  
```


Row {.tabset .tabset-fade}
-------------------------------------
   
### Spatial Distribution by Job Type

```{r by Job Type}


new3 <- df %>%
  select(c(Country, country_code, `Job Type`)) %>%
  group_by(country_code, `Job Type`) %>%
  count(Country)%>%
  ungroup() %>%
  group_by(`Job Type`) %>% 
  mutate(Percentage = percent(n/sum(n))) %>%
  ungroup()

fig2 <- plot_ly(new3, type='choropleth', locations=new3$country_code, z=new3$Percentage, text=~paste('Country: ', 
                                                                                                 new3$Country, '<br> Count: ', new3$n, '<br> Percentage: ',new3$Percentage),hoverinfo = 'text', colorscale="Viridis") %>%
                add_trace(
            transforms = list(
              list(
                type = "filter",
                target = ~`Job Type`,
                operation = 'in',
                value = unique(new3$`Job Type`)
              )
            )
  ) %>%
  layout( title = "Spatial Distribution of Proportion of Advertisments of each Job type - 2021",
    updatemenus = list(
      list(
        type = 'dropdown',
        active = 0,
        buttons = list(
          list(method = "restyle",
               args = list("transforms[0].value", unique(new3$`Job Type`)[5]),
               label = "Data Scientist"),
          list(method = "restyle",
               args = list("transforms[0].value", unique(new3$`Job Type`)[3]),
               label = "Data Analyst"),
          list(method = "restyle",
               args = list("transforms[0].value", unique(new3$`Job Type`)[4]),
               label = "Data Engineer"),
          list(method = "restyle",
               args = list("transforms[0].value", unique(new3$`Job Type`)[6]),
               label = "Statistician"),
          list(method = "restyle",
               args = list("transforms[0].value", unique(new3$`Job Type`)[2]),
               label = "BI/BA"),
          list(method = "restyle",
               args = list("transforms[0].value", unique(new3$`Job Type`)[1]),
               label = "Other")
        )
      )
    )
  )


fig2

```   
 
### Spatial Distribution of Salary

*The minimum annual salary of each country in USD
    
```{r}

new2 <- df %>%
  select(c(Country, country_code, Salary)) %>%
  group_by(Country) %>%
  mutate(Mean = mean(Salary, na.rm=TRUE)) %>%
  mutate(Mean_in_K = round(Mean/1000,2))

fig3 <- plot_ly(new2, type='choropleth', locations=new2$country_code, z=new2$Mean, text=~paste('Country: ', new2$Country, '<br> Salary (in thousands) ',new2$Mean_in_K),
                hoverinfo = 'text',colorscale="Viridis") %>%
                layout(title = "Spatial Distribution of Salary* of Job Advertisments - 2021")

fig3

```


Job Fields
======================================================

```{r janith, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(DSjobtracker)
theme_set(theme_minimal())
data("DStidy_2021")
df <- DStidy_2021
# df <- read_csv("DStidy.csv") %>% 
#   mutate(Job_Field = str_replace(Job_Field,"Information technology","IT"))
# TODO R & Python by Job Field
# TODO Job Field Minimum years of experience and location
```

Column
--------------------------------------------------------------
### Composition of Job Fields

```{r}
jf_counts <- df %>%
  count(Job_Field) %>% 
  mutate(Job_Field = fct_reorder(factor(Job_Field),n)) 

l <- levels(jf_counts$Job_Field)

jf_counts %>% 
  mutate(Job_Field = fct_relevel(Job_Field,c("Other",l[l != "Other"]))) %>% 
  ggplot(aes(x = Job_Field,y = n))+
  geom_bar(stat="identity")+
  coord_flip()
```

Column {.tabset .tabset-fade}
--------------------------------------------------------------
### R and Python Requirements of Job Fields

```{r}
df %>% 
  group_by(Job_Field) %>% 
  summarize(Total = sum(R) + sum(Python),
            R= sum(R)*100/Total,Python = sum(Python)*100/Total) %>%
  ungroup() %>% 
  mutate(Job_Field = fct_reorder(Job_Field,R)) %>% 
  pivot_longer(cols= c("R","Python"), names_to = "Language",values_to = "Counts") %>% 
  ggplot(aes(x = Job_Field,y=Counts,fill=Language))+
  geom_bar(stat="identity") + 
  coord_flip() + 
  theme(legend.position = "bottom")+
  scale_fill_manual(values = c("#306998","#919198")) + 
  labs(x = "Job Field",y = "Percentage Proportion within Job Field")
```

### Tableau and Microsoft Power BI Requirements of Job Fields

```{r}
df %>% 
  group_by(Job_Field) %>% 
  summarize(Total = sum(Tableau) + sum(`Microsoft Power BI`),
            Tableau= sum(Tableau)*100/Total,`Microsoft Power BI` = sum(`Microsoft Power BI`)*100/Total) %>%
  ungroup() %>% 
  mutate(Job_Field = fct_reorder(Job_Field,Tableau)) %>% 
  pivot_longer(cols= c("Tableau","Microsoft Power BI"), names_to = "Language",values_to = "Counts") %>% 
  ggplot(aes(x = Job_Field,y=Counts,fill=Language))+
  geom_bar(stat="identity") + 
  coord_flip() + 
  theme(legend.position = "bottom")+
  scale_fill_manual(values = c("#ffba01","#c7233b")) + 
  labs(x = "Job Field",y = "Percentage Proportion within Job Field")
```

### Minimum experience needed in Job Fields

```{r}
df %>% 
  # group_by(Job_Field) %>% 
  # summarize(Average_Min_Exp = mean(`Minimum Experience in Years`,na.rm=TRUE)) %>% 
  ggplot(aes(x = Job_Field, y = `Minimum Experience in Years`))+
  geom_boxplot()+
  coord_flip()
```

English Requirement
======================================================


```{r ramidu, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
library(devtools)
library(cli)
library(tidyverse)
library(readxl)
library(janitor)
library(treemapify)
#library(treemap)
library(devtools)
#install_github("treemap", username="mtennekes", subdir="pkg")
#library(d3Tree)
library(gridExtra)
library(ggpubr)
library(stringr)
#library(randomcoloR)
library(DSjobtracker)
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
#devtools::install_github("thiyangt/DSjobtracker") 
data("DStidy_2021")
```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
#Adjustment within job field column
DStidy_2021$Job_Field[DStidy_2021$Job_Field == "E commerce (online sales)"] <- "E commerce"


#Converting the first letter to capitals within job title field
DStidy_2021 <- DStidy_2021 %>%
  mutate(Job_title = str_to_title(Job_title))
```




```{r, warning=FALSE, message=FALSE, echo=FALSE}
#Creating job category column
DStidy_2021 <- DStidy_2021 %>%
  mutate(Job_Category = case_when(
    grepl(x = DStidy_2021$Job_title, pattern = "analyst", ignore.case = TRUE) ~ "Data Analyst",
    grepl(x = DStidy_2021$Job_title, pattern = "analytics", ignore.case = TRUE) ~ "Data Analyst",
    grepl(x = DStidy_2021$Job_title, pattern = "scientist", ignore.case = TRUE) ~ "Data Scientist",
    grepl(x = DStidy_2021$Job_title, pattern = "science", ignore.case = TRUE) ~ "Data Scientist",
    grepl(x = DStidy_2021$Job_title, pattern = "engineer", ignore.case = TRUE) ~ "Data Engineer"))

```


```{r, warning=FALSE, message=FALSE, echo=FALSE}
#Recoding NA's as other within job category column
DStidy_2021$Job_Category[is.na(DStidy_2021$Job_Category)] <- "Other"

#Recoding the location column
DStidy_2021$Location[DStidy_2021$Location == "110 Healthy Way, Folosm, CA"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "USA"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "Anaheim, CA"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "Bengaluru, Karnataka, India"] <- "India"
DStidy_2021$Location[DStidy_2021$Location == "Noida,Uttar Pradesh, India"] <- "India"
DStidy_2021$Location[DStidy_2021$Location == "Bloomington, IN"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "canada"] <- "Canada"
DStidy_2021$Location[DStidy_2021$Location == "canda"] <- "Canada"
DStidy_2021$Location[DStidy_2021$Location == "Edinburgh,London,Manchester"] <- "United Kingdom"
DStidy_2021$Location[DStidy_2021$Location == "Melbone"] <- "Australia"
DStidy_2021$Location[DStidy_2021$Location == "Pennsylvania"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "santa monica,CA"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "NewYork"] <- "United States"
DStidy_2021$Location[DStidy_2021$Location == "SL"] <- NA
DStidy_2021$Location[DStidy_2021$Location == "Sri Lnaka"] <- NA
DStidy_2021$Location[DStidy_2021$Location == "Remote Work"] <- NA
DStidy_2021$Location[DStidy_2021$Location == "NA"] <- NA
DStidy_2021$Location[DStidy_2021$Location == "UK"] <- "United Kingdom"

```



```{r, warning=FALSE, message=FALSE, echo=FALSE}
#Converting selected columns to factors
fc1 <- c(8, 18)
DStidy_2021[,fc1] <- lapply(DStidy_2021[,fc1], factor)
```




## Column {data-width=500}

### English Requirement by Country
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#Renaming categories within the English Needed column
levels(DStidy_2021$`English Needed`) <- c("No", "Yes")

#2021 English requirement by country
DStidy_2021 %>%
  drop_na(Location) %>%
  ggplot(mapping = aes(x = Location, fill = `English Needed`)) +
  geom_bar(position = "fill") +
  stat_count(geom = "text", mapping = aes(label = stat(count)),
             position = position_fill(vjust = 0.5), colour = "white") +
  labs(x = "Country", y = "Proportion") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position = "top") +
  coord_flip()

```


## Column {data-width=500, .tabset}

### English Requirement by Job Field
```{r, echo=FALSE, warning=FALSE, message=FALSE}
DStidy_2021 %>%
  drop_na(Job_Field) %>%
  ggplot(mapping = aes(x = Job_Field, fill = `English Needed`)) +
  geom_bar(position = "fill") +
  stat_count(geom = "text", mapping = aes(label = stat(count)),
             position = position_fill(vjust = 0.5), colour = "white") +
  labs(x = "Job Field", y = "Proportion") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position = "top") +
  coord_flip()

```


### English Requirement by Job Category
```{r, echo=FALSE, warning=FALSE, message=FALSE}
DStidy_2021 %>%
  drop_na(Job_Category) %>%
  ggplot(mapping = aes(x = Job_Category, fill = `English Needed`)) +
  geom_bar(position = "fill") +
  stat_count(geom = "text", mapping = aes(label = stat(count)),
             position = position_fill(vjust = 0.5), colour = "white") +
  labs(x = "Job Category", y = "Proportion") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), legend.position = "top") 

```


Soft Skills
======================================================

```{r maleesha, include=FALSE}
library(viridis)
data("DStidy_2021")
data <- DStidy_2021
```

Column {data-width=350}
-----------------------------------------------------------------------

### Composition of demanded Soft Skills

```{r}
data %>% 
  summarize(Presentation_Skills = sum(Presentation_Skills),
            Communication = sum(Communication),
            Team_Handling = sum(Team_Handling),
            Problem_Solving = sum(Problem_Solving)) %>% 
  pivot_longer(c("Presentation_Skills","Communication",
                 "Team_Handling","Problem_Solving"),names_to = "Soft skills",values_to = "Counts") %>% 
   mutate(`Soft skills` = fct_reorder(`Soft skills`,Counts)) %>% 
  ggplot(aes(x = `Soft skills`,y = Counts))+
  geom_bar(stat="identity", fill= "#0072B2")+
  coord_flip()
```

Column {data-width=650}
-----------------------------------------------------------------------

### Demanded Soft Skills according to the Job Field

```{r,fig.width=11,fig.height=9}
data %>% 
  group_by(Job_Field) %>% 
  summarize(Presentation_Skills = sum(Presentation_Skills),
            Communication = sum(Communication),
            Team_Handling = sum(Team_Handling),
            Problem_Solving = sum(Problem_Solving)) %>% 
  pivot_longer(c("Presentation_Skills","Communication",
                 "Team_Handling","Problem_Solving"),names_to = "Soft skills",values_to = "Counts") %>% 
  ggplot(aes(y = `Soft skills`,x = `Job_Field`,fill=Counts),color="white")+
  geom_tile()+
  scale_fill_viridis()+
  geom_label(aes(label = Counts),color="white") + 
  coord_flip()
```


Experience
======================================================



```{r}
## Packages
library(tidyverse)
library(plotly)
library(DSjobtracker)
```


```{r}
## Install the data set
data("DStidy_2021")

```

column{}
----------------------------------------------------------------------

### Distribution of Minimun Years of Experience

```{r}
plot_ly(DStidy_2021,
        x = ~`Minimum Experience in Years`,
        type = "histogram") %>%
  layout(xaxis = list(title = "Minimum Required Experience in Years"),
         yaxis = list(title = "No of Job Advertisements"), 
         showlegend = FALSE)
```

column{.tabset}
-----------------------------------------------------------------------

### Distribution of Experience by Job Category


```{r}
data_exp <- DStidy_2021 %>% filter(Job_Category != "Others")
plot_ly(data_exp,
        x = ~Job_Category,
        y = ~`Minimum Experience in Years`,
        type = "box",
        color = ~Job_Category,
        colors = c("#1b9e77", "#d95f02", "#7570b3", "#e7298a")) %>%
  layout(xaxis = list(title  = "Job Category", tickangle = 0),
         yaxis = list(title = "Minimum Required Experience in Years"), showlegend = FALSE)
```


### Distribution of Experience by Educational Qualifications

```{r}
data <- DStidy_2021
data_new <- pivot_longer(data, c(110:112), names_to = "Education", values_to = "Value")


data_new <- data_new %>% filter(Value == "Yes")
plot_ly(data_new,
        x = ~Education,
        y = ~`Minimum Experience in Years`,
        type = "box",
        color = ~Education,
        colors = c("#e41a1c", "#377eb8", "#4daf4a")) %>%
  layout(xaxis = list(title  = "Minimum Educational Qualifications", tickangle = 0),
         yaxis = list(title = "Minimum Required Experience in Years"), showlegend = FALSE)

```


Software and Skills
======================================================


```{r nimthera, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(treemapify)
library(DSjobtracker)
```

Column
-----------------------------------------------------------------------

```{r}

Top_skills_required<- DStidy_2021%>%
  select(c(AI:Web_Analytic_tools)) %>%
  pivot_longer(c(AI:Web_Analytic_tools), values_to = "Value", names_to = "Name") %>%
  group_by(Name) %>%
  summarize(Total = sum(Value)) %>% 
  arrange(Total) 
  
  Top_skills_required %>%
  mutate(Name = factor(Name, levels = .$Name)) %>%
  top_n(20) %>%
plot_ly(
        x= ~Total,
        y= ~reorder(Name,Total),
        type = "bar",
   marker = list(color = "hsl(0,100%,50%))") ,height = 600,width = 700)  %>% 
 
layout(title = "Top 20 Skills Required in Jobs",xaxis = list(title = "No of Job Advertisments"),
         yaxis =list(title = "Skills Required"))
```

Column
-----------------------------------------------------------------------

```{r}

 Soft_skills_required<- DStidy_2021%>%
  select(c(Presentation_Skills:`agile execution`)) %>%
  pivot_longer(c(Presentation_Skills:`agile execution`), values_to = "Value", names_to = "Name") %>%
  group_by(Name) %>%
  summarize(Total = sum(Value)) %>% 
  arrange(Total) 

Soft_skills_required %>%
  plot_ly(labels = ~Name,
          values = ~Total,
          parents = NA,
          type = "treemap", height = 600, width = 650) %>%
  layout(title = "Soft Skills Required in Jobs")

```


Software Skills
======================================================


```{r abishanya, include=FALSE}

library(flexdashboard)
library(tidyverse)
library(plotly)
library(DSjobtracker)
data("DStidy_2021")
```

Column {data-width=500}
-----------------------------------------------------------------------

### Statistical softwares


```{r}

Statistical_software <- paste(DStidy_2021$R,DStidy_2021$SAS,DStidy_2021$SPSS,DStidy_2021$Python,sep = "::")


d1 <- Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]

Statistical_software[Statistical_software=="1::0::0::0"] <-"R only"
Statistical_software[Statistical_software=="0::0::0::1"] <-"Python only"
Statistical_software[Statistical_software=="0::1::0::0"] <-"SAS only"
Statistical_software[Statistical_software=="1::0::0::1"] <-"R & Python"
Statistical_software[Statistical_software=="1::1::0::1"] <-"R, SAS & Python only "
Statistical_software[Statistical_software=="0::0::0::0"] <-"No statistical softwares"
Statistical_software[Statistical_software=="0::1::0::1"|Statistical_software=="1::1::1::1" |Statistical_software=="0::1::1::1"|Statistical_software=="1::1::1::0"|Statistical_software=="1::1::0::0"] <- "Other statistical softwares"


d1 <- Statistical_software %>% table() %>% as.data.frame()
names(d1) <- c('Statistical_software', 'Frequency')
d1 <- d1[order(d1$Frequency, decreasing = T),]


d1 %>% plot_ly(x = ~Frequency, y = ~reorder(Statistical_software, Frequency), type =  'bar', orientation = 'h') %>% layout(title = "",xaxis = list(title = "Number of job advertisements" ,zeroline = FALSE), yaxis = list(title = "", zeroline = FALSE))
```

Column {data-width=500}
-----------------------------------------------------------------------

### Database and Query languages

```{r}
Database_and_Query_languages <- paste(DStidy_2021$SQL,DStidy_2021$NoSQL,DStidy_2021$MySQL,DStidy_2021$Hadoop,sep = "::")


d2 <- Database_and_Query_languages %>% table() %>% as.data.frame()
names(d2) <- c('Database_and_Query_languages', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]


Database_and_Query_languages[Database_and_Query_languages=="1::0::0::0"] <-"SQL only"
Database_and_Query_languages[Database_and_Query_languages=="1::0::1::0"] <-"SQL & MySQL"
Database_and_Query_languages[Database_and_Query_languages=="1::0::0::1"] <-"SQL & Hadoop"
Database_and_Query_languages[Database_and_Query_languages=="1::1::0::0"] <-"SQL & NoSQL"
Database_and_Query_languages[Database_and_Query_languages=="0::0::0::0"] <-"No database or query languages"

Database_and_Query_languages[Database_and_Query_languages=="0::0::1::0"|Database_and_Query_languages=="0::1::0::0" | Database_and_Query_languages=="0::0::0::1"| Database_and_Query_languages=="1::1::1::1" | Database_and_Query_languages=="1::1::0::1"| Database_and_Query_languages=="1::0::1::1"| Database_and_Query_languages=="1::1::1::0"] <- "Other"


d2 <- Database_and_Query_languages %>% table() %>% as.data.frame()
names(d2) <- c('Database_and_Query_languages', 'Frequency')
d2 <- d2[order(d2$Frequency, decreasing = T),]


d2 %>% plot_ly(x = ~Frequency, y = ~reorder(Database_and_Query_languages, Frequency), type =  'bar', orientation = 'h', color = "red") %>% layout(title = "",xaxis = list(title = "Number of job advertisment" ,zeroline = FALSE), yaxis = list(title = ""))


```


Knowledge and Skills

======================================================


```{r theja, include=FALSE}
library(readr)
library(plotly)
library(gganimate)
library(ggpubr)

```

# Knowledge and Skills

Column {data-width=650}
-----------------------------------------------------------------------

### Treemap of Konwledge and skills

```{r}
ks<-DStidy_2021%>%select(c(AI:Data_translation,Presentation_Skills:Payroll_management))
df<-ks%>%pivot_longer(1:31,"Knowledge_and_skills","Cases")%>%group_by(Knowledge_and_skills) %>%summarize(No_of_Job_vacancies = sum(value))%>%mutate(parents="Knowledge and Skills") 
df%>%plot_ly(type="treemap",labels=~Knowledge_and_skills,parents=~parents,values=~No_of_Job_vacancies,domain=list(column=0),textinfo="label+value+percent parent")
```

Column {data-width=350}{.tabset .tabset-fade}
-----------------------------------------------------------------------

### Required Knowledge according to job category

```{r}
Job_Titles <- str_to_lower(DStidy_2021$Job_title)
Job_Titles <- str_trim(Job_Titles)
Job_Titles <- str_replace_all(Job_Titles,",|-|/", " ")


Job_Titles <-  Job_Titles %>% str_replace_all("analyzt", "analyst") 
Job_Titles <-  Job_Titles %>% str_replace_all("acturial", "actuarial")


DS <- Job_Titles[str_detect(Job_Titles, "([data]{4}|machine)[&a-z\\s]*([scientist]{7,10})|\\s+ai")] %>% unique() 

DE <- Job_Titles[str_detect(Job_Titles, "([data]{4}|machine|intelligence)[&a-z\\s]*([engineer]{8,9})")] %>% unique()


DA <- Job_Titles[str_detect(Job_Titles, "anal|statist|actuarial|research|statician")] %>% unique()
DA <- DA %>% append(Job_Titles[!(Job_Titles%in%c(DS,DE,DA))] %>% unique() %>% .[str_detect(.,"data\\s+")]) 
DS <- DS %>% append(Job_Titles[!(Job_Titles%in%c(DS,DE,DA))] %>% unique() %>% .[str_detect(.,"machine\\s+")])

DA <- DA[!DA%in%DS]
DA <- DA[!DA%in%DE]
DS<-DS[!DS%>%is.na()]
DE<-DE[!DE%>%is.na()]
Unimportant <- Job_Titles[!(Job_Titles%in%c(DS,DE,DA))] %>% unique()


DStidy_2021  <- DStidy_2021 %>% mutate(Job_Titles, Job_Category= ifelse(Job_Titles%in%DS & Job_Titles%in%DE, "Data Science and Data Engineering", ifelse(Job_Titles%in%DS, "Data Science", ifelse(Job_Titles%in%DA,"Data Analyst", "Other" ) ) )) 

df1<-DStidy_2021%>%select(c(AI:Data_translation,Data_marketing:Payroll_management,Job_Category))%>%pivot_longer(1:26,"Knowledge","Cases") %>%filter(value=="1")%>%group_by(Knowledge,Job_Category)%>%count()
p2<-ggdotchart(df1,x="Knowledge",y="n",color = "Job_Category",palette = c("#00AFBB","#E7B800","#FC4E07","#FF1493","#7FFFD4"),sorting = "asc",sort.by.groups=TRUE,add="segments",add.params = list(color="lightgray",size=2),dot.size = 4,ggtheme =theme_pubclean())+ font("x.text",size=8,vjust=0.5)+labs(x="Required Knowledge ",y="Count")
ggpar(p2,legend.title = "")%>%ggplotly()%>%layout(legend=list(orientation="h",xanchor="center",x=0.5,y=1.6))

```

### Required Skills according to job category


```{r}
df2<-DStidy_2021%>%select(c(Presentation_Skills:"agile execution",Job_Category))%>%pivot_longer(1:5,"Skills","Cases") %>%filter(value=="1")%>%group_by(Skills,Job_Category)%>%count()
p3<-ggdotchart(df2,x="Skills",y="n",color = "Job_Category",palette = c("#00AFBB","#E7B800","#FC4E07","#FF1493","#7FFFD4"),sorting = "asc",sort.by.groups=TRUE,add="segments",add.params = list(color="lightgray",size=2),dot.size = 4,ggtheme =theme_pubclean())+ font("x.text",size=8,vjust=0.5)+labs(x="Required Skills ",y="Count")
ggpar(p3,legend.title = "")%>%ggplotly()%>%layout(legend=list(orientation="h",xanchor="center",x=0.5,y=1.6))
```




```{r silaxsha, include=FALSE}
library(flexdashboard)
library(plotly)
library(dplyr)
```

```{r data}
data_new <- read.csv("datamod.csv")

```

# Education

Column {data-width=200, .tabset}
-----------------------------------------------------------------------

### Educational Qualifications

```{r}
data1 <- data_new %>% group_by(Educational_qualifications) %>% summarise(n = n())

fig1 <- plot_ly(x = data1$n,y = data1$Educational_qualifications,type = "bar", color = data1$Educational_qualifications, domain = list(x = c(0, 0.5), y = c(0, 1))) %>% 
  layout(yaxis = list(categoryorder = "total ascending"))
fig1
```




```{r ann, include=FALSE}
library(flexdashboard)
library(plotly)
library(tidyverse)
library(DT)
library(shiny)


```
Salary {}
=====================================

Row
-------------------------------------

### Distibution of Average of Minimum Salaries by Job 

```{r}

devtools::install_github("thiyangt/DSjobtracker")
library(DSjobtracker)

data("DStidy_2021")

df <- DStidy_2021

df_1 <- subset(df, df$Salary < 250000)



   plot_ly(df_1,
              x = df_1$Salary,
              color = df_1$Job_Category,
              colors = "Paired",
              type = "box") %>%
  layout(title = "",
         xaxis = list(title = "Yearly Salary in USD" ,
                      zeroline = FALSE))


```


Row
------------------------------------
### Distibution of Average of Minimum Salaries by Countries

```{r}

  
   plot_ly(df_1,
              x = df_1$Salary,
              color = df_1$Country,
              colors = "Paired",
              type = "box") %>%
  layout(title = "",
         xaxis = list(title = "Yearly Salary in USD" ,
                      zeroline = FALSE))

```


Our Team
======================================================



Project Supervisor: [Dr Thiyanga S. Talagala](https://thiyanga.netlify.app/)

**Dashboard Panels**

Overview: Heshani Achinthika

Spatial Distributions: Rashmini Rathnaweera

Job Field: Janith Wanniarachchi

English Requirement: Ramindu De Silva

Soft Skills: Maleesha Panangala

Experience: Randi Shashikala

Software and Skills: Nimthara Gamage

Software Skills: Abishanya Sundharampillai

Knowledge and skills: Theja Sanduni

Education: Silaxsha Punniyamoorthy

Salary: Ann Shehani



Compilation of all panels: Dr Thiyanga Talagala

**Data Collection**


Heshani Achinthika, Rashmini Rathnaweera, Janith Wanniarachchi, Ramindu De Silva,   Maleesha Panangala, Randi Shashikala, Ann Shehani, Nimthara Gamage, Abishanya Sundharampillai, Theja Sanduni, Silaxsha Punniyamoorthy



**R package development co-authors/ contributors**

Dr Thiyanga Talagala

Janith Wanniarachchi 

Randi Shashikala







